%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

\setmainfont{Lato}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{img/LG.png}
\name{Laura }{Gomez}
\position{System Engineer{\enskip\cdotp\enskip}Mechatronics and Biomedical engineer}
\address{Antony, France}

\mobile{(+33) 7 70 49 23 44}
\email{laura-gomez@gmx.fr}
%\homepage{www.posquit0.com}
%\github{posquit0}
\linkedin{laura-gomez-0a547158}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

\quote{``Millons saw the apple fall but Newton asked why. Bernard Baruch"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Johnson \& Johnson}
 % {City\\Switzerland}
  {Switzerland}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Technical Project Manager}
% How the letter is opened
\letteropening{Dear Sir or Madam,}
% How the letter is closed
\letterclosing{Best Regards,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}

%-------------------------------------------------------------------------------
\begin{document}
% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Laura Gomez~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

%\lettersection{Introduction}

Passionate, curious and with an analytical mindset, I love finding solutions to help people stay healthy and improve their daily lives.
That is why I chose to complet two masters. One in mechatronics engineering and the second one on a research master's in biomechanical with a specialization in biomechanics. 

The mechatronics is the interface of the three domains of robotics. Namely the mechanics, the automatics and the software.
I chose to add a fourth domain to it (the more complex in my opinion), Human. As I could see during my career, the complexity of the interaction between a system and us, humans is high by two aspects.
First of all, the body is a complex system, as I could experiment during my research for the CEA, working in a sluterhouse. But the comfort and the social aspect are also to take into account and depends on an incredible high number of parameters.
But the research in new technologies is the fastest way to improve the daily life of patients.

During my experience in research and industrial product development, I had the chance to cover all phases of new products and update of industrialized ones.
From the understanding of the need (biomechanical study) to the concept, design, prototyping, validation and manufacturing leading. 

In fact, during my career, I had some great experiences as a technical project leader. 
Following a product's lifecycle from the customer's requirements to its delivery and working closely with all the internal and external stakeholders.
In particular, I can take as an example my experience at Zodiac's as a technical project manager. 
I was the technical reference for our Italian client and my role was to translate the client's requirements into technical specifications, in accordance with the different R\&D Managers (Mechanical, Electronical and Software team leaders).
In collaboration with the team leaders, I established the different deadlines and set the priorities to be able to fit to the client's planning, as well as, that of our R\&D teams.
In addition to the organizational part, I asked to perform tests when derisking was necessary, and I conceved a harness to confrom to the client's needs regarding the electronical parts to control, the dimensions required and the path it would take through the airplane seats.
When the first system was completed, I went to test it with a software engineer at the client's site, in order to validate the results.

Highly adaptable, methodical and proactive, you will be able to count on me to support the R\&D and Project Managers as well as the Sales and Marketing Teams
to lead the project to succes in a cross-functional and cross-cultural environment.

Motivated to be part of an international and innovative team I would be thrilled to join Johnson \& Johnson to continue to learn and grow while contributing in delivering impactful products to patients worldwide.
%I would be thrilled to learn more about this job opening. Thank you for your time and I look forward to hearing from you.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing


\end{document}
